---
usethis::use_github()---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MeaslesMapR)
```

### plotCases

```{r}
#| label: plotCases

# plotCases
plotCases(region, legend = F)
```

When provided with region(s) and an optional legend specification, plotCases generates a line plot displaying the total cases for countries in the regions.
 Valid regions include "Africa," "Americas," "Eastern Mediterranean," "Europe," "South East Asia," and "Western Pacific."


### summarizeYear

```{r}
#| label: summarizeYear

# summarizeYear
summarizeYear(year)
```

When provided with a year, summarizeYear generates a table where each row represents a region along with its average measles cases per million and the country with the highest number of cases for that year.

### summarizeRegion

```{r}
#| label: summarizeRegion

# summarizeRegion
summarizeRegion(region)
```

When provided with a region, summarizeRegion generates a table where each row represents one country in the region and its measles cases count per million over each year in the data.

### validateRegion

```{r}
#| label: validateRegion

# validateRegion
validateRegion(region, data)
```

A helper function that when given a region name and a data frame, checks whether the data frame contains data for that region. Valid regions include "Africa," "Americas," "Eastern Mediterranean," "Europe," "South East Asia," and "Western Pacific"

### validateYear

```{r}
#| label: validateYear

# validateYear
validateYear(year1, year2 = NULL)
```

A helper function that given two years, checks that the years are actual years.

### modelCases

```{r}
#| label: modelCases

# modelCases
modelCases(interaction = T)
```

Runs a model and displays summary output for a generalized linear negative binomial model with total measles as the response
